Visual Inference for Networks

### 2016-07-12 JSM/VizInfSlides.Rmd
small amount more about estimation
start slides

@@

@@

>>>>

## Lineup (?)

@@

Goal: modeling dynamic networks using

- Network effects (e.g. outdegree, reciprocity)
- Actor covariate effects

## Model "Rules"

Observed networks treated as discrete observations of a continuous time Markov Chain.

1. At each (unobserved) time point in the CTMC one actor can change one of its ties.
2. Between network observations (say from $t_1$ to $t_2$) all actors are given the opportunity to change a tie at the same rate.
3. Once an actor can change, it tries to maximize its objective functon, $f_i(x)$
Parameters:

@@

## References

## Thank you!
